\documentclass[11pt,a4paper]{exam}
\usepackage{amsmath,amsfonts,amssymb,graphicx}
\usepackage[margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{datetime}

% Header and Footer
\pagestyle{headandfoot}
\firstpageheader{\textbf{Class VIII Mathematics}}{}{\textbf{Model Question Paper}}
\runningheader{Class VIII Mathematics}{}{\textbf{Model Question Paper}}
\firstpagefooter{}{Page \thepage\ of \numpages}{}
\runningfooter{}{Page \thepage\ of \numpages}{}

% Section formatting
\titleformat{\section}{\large\bfseries\filcenter}{}{0em}{}
\newcommand{\SCHOOLNAME}{GUIDELY}
\begin{document}
	
	\begin{center}
		\Large\textbf{\SCHOOLNAME} \\
		\large\textbf{MATHEMATICS} \\
		\textbf{Class VIII} \\
		\textbf{Maximum Marks: 50 \hspace{2cm} Time: 1 Hour 30 Minutes} \\
		\rule{\textwidth}{1pt}
	\end{center}
	
	\section*{General Instructions:}
	\begin{enumerate}
		\item All questions are compulsory.
		\item The question paper consists of 4 sections (A, B, C, D).
		\item Section A contains 6 questions of 1 mark each.
		\item Section B contains 4 questions of 2 marks each.
		\item Section C contains 5 questions of 3 marks each.
		\item Section D contains 3 questions of 5 marks each.
		\item Use of calculators is not permitted.
	\end{enumerate}
	
	\section*{Section A (1 mark each)}
	\begin{questions}
		\question Evaluate: $(-2)^3 \times (-2)^2$
		\question What is the sum of the angles of a regular pentagon?
		\question Simplify: $3x + 2y - x + 5y$
		\question Find the value of $\sqrt{0.09}$
		\question If a number is tripled and then decreased by 7, the result is 20. Write the equation.
		\question What is the probability of getting a prime number when a die is rolled?
	\end{questions}
	
	\section*{Section B (2 marks each)}
	\begin{questions}
		\question Solve for $x$: $\dfrac{2x-3}{4} = \dfrac{x+1}{3}$
		\question Find the area of a rhombus whose diagonals are 6 cm and 8 cm.
		\question Factorize: $x^2 + 5x + 6$
		\question The angles of a quadrilateral are in the ratio 1:2:3:4. Find all the angles.
	\end{questions}
	
	\section*{Section C (3 marks each)}
	\begin{questions}
		\question Construct a quadrilateral ABCD where AB = 5 cm, BC = 4 cm, CD = 6 cm, DA = 4.5 cm and AC = 7 cm.
		\question A sum of money doubles itself in 5 years at simple interest. What is the rate of interest?
		\question Solve the linear equation: $3(2x-1) + 2(3x+2) = 5$
		\question Draw the graph of the equation $y = 2x + 3$ for values of $x$ from -2 to 2.
		\question The volume of a cube is 343 cm$^3$. Find its total surface area.
	\end{questions}
	
	\section*{Section D (5 marks each)}
	\begin{questions}
		\question A rectangular field is 50 m long and 30 m wide. A path of uniform width runs around the field inside it. If the area of the path is 456 m$^2$, find its width.
		\question The pie chart shows the distribution of 600 students in different activities:
		\begin{itemize}
			\item Sports: 120°
			\item Music: 60°
			\item Reading: 90°
			\item Art: 30°
			\item Others: 60°
		\end{itemize}
		Find the number of students engaged in each activity.
		\question In a right-angled triangle ABC, right-angled at B, AB = 6 cm and BC = 8 cm. A circle is inscribed in the triangle. Find the radius of the circle.
	\end{questions}
	
	\begin{center}
		\textbf{--- End of Question Paper ---}
	\end{center}
	
\end{document}